Self-Supervised Transfer Learning From 2D Images to 3D Point Clouds

### 2022-05-14 doc/paper.tex
adds caption to overview diagram

@@

\begin{figure}
    \centering
    %angle=-90,origin=c
    \includegraphics[width=8.5cm]{images/overview.pdf}
    \caption{Overview of }
    \label{fig:overview}
\end{figure}

>>>>

Labeling effort: SemanticKITTI had 518 tiles of 100m x 100m and took 4.5 hours per residential tile and 1.5 hours per highway. Total of 1700 hours. Scannet took 20 people 1 month just to capture data.

@@

\begin{figure}
    \centering
    \includegraphics[width=8.5cm]{images/overview.pdf}
    \caption{
        \textbf{Overview of our pre-training pipeline.} \textbf{Stage 1:} A 2D model is pre-trained by applying a contrastive infoNCE loss on two augmentations of a single image at pixel level. \textbf{Stage 2:} The same loss is applied on the outputs of the pre-trained 2D model and raw 3D model by mapping the point features into the image. Above, black represents the sample query point, while green represents the positive point and red represents negative points to be contrasted against.
    }
    \label{fig:overview}
\end{figure}
